---
output: 
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-")
```
## Overview

`"binomial"` is an R package that provides functions to make different calculations on a Binomial random variable.  

- `bin_choose()` calculates the number of combinations in which `k` successes can occur in `n` trials    
- `bin_probability()` calculates the probability of getting `k` successes in `n` trials    
- `bin_distribution()` creates a data frame after calculating the probability of each value of success in n trials with the columns success and probability    
- `plot()` method for `bin_distribution()` to make a barplot of the probability of each value of success in n trials    
- `bin_cumulative()` create a data frame after calculating cumulative probability of each value of success in n trials with the columns success, probability, and cumulative    
- `plot()` method for `bin_cumulative()` to plot the cumulative probability in a line graph    
- `bin_variable()` creates a named list for trials and probability    
- `print()` method for `bin_variable()` to print out the number of trials and probability    
- `summary()` method for `bin_variable()` to calculate the five different measures of a binomial distribution and put it in a named list    
- `print.summary()` method for `bin_variable()` to print out the number of trials and probability along with the five different measures    


## Motivation

This assignment involves learning how to create an R package using devtools and testthat packages. 


## Installation
Install the development version from GitHub via the package "devtools":
```{r}
# development version from GitHub:
#install.packages("devtools")

# install "binomial" (without vignettes)
#devtools::install_github("stat133-sp19/hw-stat133-melodyjt/tree/master/workout3/binomial")

# install "binomial" (with vignettes)
#devtools::install_github("stat133-sp19/hw-stat133-melodyjt/tree/master/workout3/binomial", build_vignettes = TRUE)

```

## Usage
```{r}
# Usage
library(binomial)

bin_choose(n = 5, k = 2)

bin_probability(success = 2, trials = 5, prob= 0.5)

bin_distribution(trials = 5, prob = 0.5)

dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)

bin_cumulative(trials = 5, prob = 0.5)

dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)

bin_variable(trials = 10, prob = 0.3)

summary(bin_variable(trials = 10, prob = 0.3))
```


